%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Freeman Curriculum Vitae
% XeLaTeX Template
% Version 2.0 (19/3/2018)
%
% This template originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Vel (vel@LaTeXTemplates.com)
% Alessandro Plasmati
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%!TEX program = xelatex
% NOTICE: This template must be compiled with XeLaTeX, the line above should
% ensure this happens automatically but if it doesn't you will need to specify 
% XeLaTeX as the engine in your editor or script
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[12pt]{article} % Font size, can be: 10pt, 11pt or 12pt

\input{structure.tex} % Include the file that specifies the document structure

% Headers and footers can be added with the \lhead{} \rhead{} \lfoot{} \rfoot{} commands
% Example right footer:
%\rfoot{\color{headings}{\sffamily Last update: \today. Typeset with Xe\LaTeX}}

%----------------------------------------------------------------------------------------
%	 PERSONAL INFORMATION
%----------------------------------------------------------------------------------------

% If you don't need one or more of the below, just remove the content leaving the command, e.g. \cvnumberphone{}

\profilepic{} % Profile picture

\cvname{Khalil Al Handawi, PhD} % Your name
\cvjobtitle{Engineer, designer, and researcher} % Job title/career

\cvdate{} % Date of birth
\cvaddress{Montr\'{e}al Qu\'{e}bec, Canada} % Short address/location, use \newline if more than 1 line is required
\cvnumberphone{+1 (514) 572-7367} % Phone number
\cvsite{sol.research.mcgill.ca} % Personal website
\cvmail{khalil.alhandawi@mail.mcgill.ca} % Email address
\cvgithub{github.com/khbalhandawi} % GitHub
\cvlinkedin{linkedin.com/in/khbalhandawi} % LinkedIn

\aboutme{I believe that physics and artificial intelligence should be two sides of the same coin. One cannot exist without the other. How? By cross-validation. In this way, the toughest physics and mathematics problems can be solved! This philosophy is what drives my research.} % To have no About Me section, just remove all the text and leave \aboutme{}

\begin{document}

\begin{paracol}{2} % Begin the multi-column environment

%----------------------------------------------------------------------------------------
%	NAME AND CURRICULUM VITAE TEXT
%----------------------------------------------------------------------------------------

\parbox[top][0.1\textheight][c]{\linewidth}{ % Parbox to hold the author name and CV text; fixed height to match the coloured box to the right, centred vertically and full line width
	\vspace{0.0\textheight} % Reduce whitespace above the parbox to separate it from the main content
	\centering % Centre text
	{\sffamily\LARGE \cvname}\\\medskip % Your name
}

%----------------------------------------------------------------------------------------

\switchcolumn % Switch to the next paracol column

%----------------------------------------------------------------------------------------
%	COLOURED CONTACT DETAILS BOX
%----------------------------------------------------------------------------------------

\parbox[top][0.1\textheight][c]{\linewidth}{ % Parbox to hold the colour box; fixed height to match the name/CV text to the left, centred vertically and full line width
	\vspace{0\textheight} % Reduce whitespace above the parbox to separate it from the main content
	\colorbox{shade}{ % Create the coloured box
		\begin{supertabular}{p{0.05\linewidth}|p{0.775\linewidth}} % Start a table with two columns, the table will ensure everything is aligned
			\ifthenelse{\equal{\cvdate}{}}{}{\raisebox{-1pt}{\faInfo} & \cvdate \\}
			\ifthenelse{\equal{\cvaddress}{}}{}{\raisebox{-1pt}{\faHome} & \cvaddress \\} % Address
			\ifthenelse{\equal{\cvaddress}{}}{}{\raisebox{-1pt}{\faPhone} & \cvnumberphone \\} % Phone number
			\ifthenelse{\equal{\cvmail}{}}{}{\raisebox{0pt}{\small\faEnvelope} & \href{mailto:\cvmail}{\cvmail} \\} % Email address
			\ifthenelse{\equal{\cvgithub}{}}{}{\raisebox{-1pt}{\faGithub} & \href{https://\cvgithub}{\cvgithub} \\} % GitHub profile
			\ifthenelse{\equal{\cvlinkedin}{}}{}{\raisebox{-1pt}{\faLinkedinSquare} & \href{https://\cvlinkedin}{\cvlinkedin} \\} % LinkedIn profile
			% See fontawesome.pdf in the fonts folder for all icons you can use
		\end{supertabular}
	}
}

\end{paracol}

\medskip % Extra whitespace before the next section
\rule[0pt]{\textwidth}{1pt}\\
%----------------------------------------------------------------------------------------
%	ADDRESS
%----------------------------------------------------------------------------------------
\today\\[6pt]
Prof. Heather MacLean\\
Department of Civil \& Mineral Engineering\\
\textit{University of Toronto}\\
35 St. George St.\\
Toronto, Ontario, Canada, M5S 1A4\\[6pt] \medskip
%----------------------------------------------------------------------------------------
%	MAIN BODY
%----------------------------------------------------------------------------------------
Dear Prof. MacLean,

% alternative powertrains and light-weighting are studied separately in the literature
% Interesting to identify causal loops in the LCA module and exploit dynamic LCA analyses
% Interesting to factor in the effects of the COVID pandemic on fleet vehicle kilometers and GHG for 2020/2021
% Multidiscplinary optimization of several submodule policies that are coordinated by the LCA module (e.g. GHG emissions vs fleet fuel use vs vehicle characteristics vs material recovery rates) Vehicle weight minimization trade-off with performance and features

\medskip % Extra whitespace before the next section 
I am very excited to learn of the opportunity to work on life cycle assessment of low carbon light-duty vehicle (LDV) technologies. I have perused your recent work and have always shared your views surrounding the rapid electrification of modern light vehicle fleets. Most countries are introducing bans within the next 30 years on internal combustion engines when in reality, they should be focusing on reducing the need to drive longer distances using heavier vehicles (such as SUVs) which has been steadily climbing in the past few years.

\medskip % Extra whitespace before the next section

Detailed life-cycle analysis of alternative technological pathways (electric vehicles, fuel cell vehicles, and powertrain technologies) are the key to formulating a policy that comprises several measures for meeting the greenhouse gas (GHG) emission targets for the next few decades. I believe that my research experience in the field of remanufacturing of aeroengine components can help enrich existing LCA models of LDV fleets. I have developed models for estimating the impact of remanufacturing on the overall performance of aeroengine components as well as algorithms and design metrics for deciding on how and when to remanufacture an existing product.

\medskip % Extra whitespace before the next section

Although my research was more oriented towards life extension of individual products and components rather than entire fleets, I feel there are some similarities involved when it comes to circular economy aspects of design. In other words, adopting a circular economy paradigm in design and policy-making by considering remanufacturing (e.g., vehicle lightweighting) alongside new technologies (such as electric vehicles) can help extract the most value from product fleets (in the form of lower lifecycle costs and GHGs).

\medskip % Extra whitespace before the next section

I realize that being a researcher entails three things: 1) Mentorship and supervision acumen 2) Strong research skills 3) Good communication skills to present key takeaways from cutting-edge research.

\medskip % Extra whitespace before the next section

I have ample experience with all three fields and thrive on mentoring and teaching my students. Nothing gives me a greater sense of joy than hearing about the accomplishments of my students. As you can tell from my career profile, I made it a habit to always engage in research and mentorship simultaneously and never turned away anyone that asks for my opinion or guidance.

\medskip % Extra whitespace before the next section

I have a strong mathematical background in research related to numerical optimization, simulation and data-driven models. I combined these three aspects to automate time-consuming simulation-based design problems in the aerospace industry and was able to transform my ideas into industrial practice through the training programs and workshops that I conducted for our industrial partners (GKN Aerospace).

\medskip % Extra whitespace before the next section

Yours sincerely,

\medskip % Extra whitespace before the next section

Khalil Al Handawi

\medskip % Extra whitespace before the next section

%----------------------------------------------------------------------------------------

\end{document}